Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-07-16 paper.Rmd
added two paragraphs ref political and operational interests on resilience.

Recently, the term is also used frequently on the political and strategic level. Policymakers, operational experts, and academes concur that the concept of resilience plays a major role when addressing and assessing the extent to which organisations and systems are prepared and capable to respond to and recover from disruptions.

@@

-   political level: ADD SOME DESCRIPTION

-   operational level: ADD SOME DESCRIPTION

>>>>

Recently, the term is also used frequently on the political and strategic level. Policymakers, operational experts, and academics concur that the concept of resilience plays a major role when addressing and assessing the extent to which organisations and systems are prepared and capable to respond to and recover from disruptions.

@@

-   political level: The continuity and sustainability of a stable air traffic system supports and affects other dimensions of political interest, such as commercial relations, tourism industry, public health policies, among others. As a result, at a political level, it is of the utmost importance that the air navigation system remains functional. In that understanding, political acts were necessary in face of the pandemic crisis effects on aviation. For example, many governments injected financial support in the airline sector in order to help  them survive the worst periods. In addition, measures such as tax deferrals to air navigation services providers were also adopted. Therefore, understanding how the air navigation system can exist in a more resilient manner is certainly beneficial for many political agents.

-   operational level: While efficiency, delay management, and capacity constraints were previously the main problems affecting resilience, now the concept must be broadened to an inverted scenario. Airlines, ANSPs, airports, and other stakeholders in the industry must remain and manage resilience not only in order to recover from disruptions caused by excessive demand, but also from insufficient demand. If delays are no longer the main threat, others arise, such as insufficient funding, lack of training, and traffic unpredictability.
